\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color}
\usepackage{comment}
\usepackage[ruled]{algorithm2e}
\usepackage{wrapfig}
\usepackage{makecell}
\usepackage{multirow}
\usepackage{microtype}
\newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}


\newcommand{\juyong}[1]{\textcolor{red}{[Juyong:~{#1}]}}
\newcommand{\bailin}[1]{\textcolor{cyan}{[Bailin:~{#1}]}}
\newcommand{\surrog}[1]{\overline{#1}}
\newcommand{\newpos}[1]{\widehat{#1}}
\newcommand{\nua}{\nu_{\textrm{a}}}
\newcommand{\nur}{\nu_{\textrm{r}}}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\proj}{proj}
\newcommand{\SOG}{\mathcal{R}}
\DeclareMathOperator{\Tr}{Tr}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{5011} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

%%%%%%%%% TITLE
\title{Quasi-Newton Solver for Robust Non-Rigid Registration}

\author{Yuxin Yao\textsuperscript{1} \quad Bailin Deng\textsuperscript{2} \quad Weiwei Xu\textsuperscript{3} \quad Juyong Zhang\textsuperscript{1}\thanks{Corresponding author}\\
	\textsuperscript{1}University of Science and Technology of China \quad \textsuperscript{2}Cardiff University\quad \textsuperscript{3}Zhejiang University\\
	{\tt\small yaoyuxin@mail.ustc.edu.cn} \quad  {\tt\small DengB3@cardiff.ac.uk}\quad  {\tt\small xww@cad.zju.edu.cn} \quad  {\tt\small juyong@ustc.edu.cn}
%Institution1\\
%Institution1 address\\
%{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
%\and
%Second Author\\
%Institution2\\
%First line of institution2 address\\
%{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
Imperfect data (noise, outliers and partial overlap) and high degrees of freedom make non-rigid registration a classical challenging problem in computer vision. Existing methods typically adopt the $\ell_{p}$ type robust estimator to regularize the fitting and smoothness, and the proximal operator is used to solve the resulting non-smooth problem. However, the slow convergence of these algorithms limits its wide applications. In this paper, we propose a formulation for robust non-rigid registration based on a globally smooth robust estimator for data fitting and regularization, which can handle outliers and partial overlaps. We apply the majorization-minimization algorithm to the problem, which reduces each iteration to solving a simple least-squares problem with L-BFGS. Extensive experiments demonstrate the effectiveness of our method for non-rigid alignment between two shapes with outliers and partial overlap, with quantitative evaluation showing that it outperforms state-of-the-art methods in terms of registration accuracy and computational speed. The source code is available at \url{https://github.com/Juyong/Fast_RNRR}.
\end{abstract}

\input{introduction}
\input{related}
\input{algorithm}
\input{results}
\input{conclusion}

\noindent \textbf{Acknowledgement}
We thank the authors of~\cite{guo2015robust} for providing their implementation.
This work was supported by the National Natural Science Foundation of China (No. 61672481), and Youth Innovation Promotion Association CAS (No. 2018495).

{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}
\input{supp}

\end{document}
